%-------------------------
% Resume in LaTeX
% Author : Sonu Kumar
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{ #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Sonu Kumar} & \href{mailto:sannyraj94@gmail.com}{sannyraj94@gmail.com} \\
  Address: Vaishali, Bihar, India-844128 & Mobile: +(91)-8709796492 \\
  \href{https://www.linkedin.com/in/sonu-94-kumar/}{LinkedIn: sonu-94-kumar} & \href{https://github.com/sonu1994roy}{GitHub: github.com/sonu1994roy} \\
\end{tabular*}

%--------Profile Summary------------
\section{Profile Summary}
\resumeSubHeadingListStart
\resumeSubItem{}{Dynamic MERN Stack Developer driven by innovation and a thirst for learning. Dedicated to crafting
seamless user experiences with expertise in React.js, Express.js, Node.js, and MongoDB. Proven
ability to adapt to evolving technologies and collaborate effectively in fast-paced environments.
}
\resumeSubHeadingListEnd

%--------Programming Skills------------
\section{Programming Skills}
\resumeSubHeadingListStart
\resumeSubItem{}{\textbf{Programming Languages:} JavaScript, TypeScript, Python, JSON, NoSQL, HTML, CSS}
\resumeSubItem{}{\textbf{Frameworks \& Libraries:} React.js, Node.js, Express.js, Next.js, Bootstrap, MaterialUI}
\resumeSubItem{}{\textbf{Tools \& Platforms:} GitHub Actions, WebRTC, Linux Servers, REST APIs, Payment Gateways, CI/CD, Redux.js, Webpack, ESLint}
\resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
{Teminos Technology Pvt Ltd}{Kolkata, India}
{Software Engineer}{07/2024 - Present}
\resumeItemListStart
\resumeItem{} {Designed scalable backend systems using Node.js, integrating MongoDB and SQL, reducing query time by 25\%.}
\resumeItem{} {Automated CI/CD pipelines with GitHub Actions, improving deployment efficiency by 40\%.}
\resumeItem{} {Implemented real-time communication systems (WebRTC, Socket.IO), enhancing user engagement by 15\%.}
\resumeItem{} {Collaborated with frontend teams, providing backend support and ensuring optimal integration and user experience.}
\resumeItem{} {Worked with third-party services like Google Maps, geolocation APIs, and payment gateways to enhance functionality.}
\resumeItem{} {Technologies: Node.js, MongoDB, SQL, Express.js, React.js, GitHub Actions, Linux Servers.}
\resumeItemListEnd

\resumeSubheading
{Gnoin Pvt Ltd}{Kolkata, India}
{MERN Stack Developer}{01/2022 - 06/2024}
\resumeItemListStart
\resumeItem{} {Developed dynamic e-commerce platforms with payment gateways, increasing user transactions by 30\%.}
\resumeItem{} {Streamlined API performance with MongoDB aggregation pipelines, reducing latency by 50\%.}
\resumeItem{} {Led frontend redesign of company portfolio websites, achieving a 20\% increase in traffic.}
\resumeItemListEnd

\resumeSubheading
{Freelance Web Developer}{Patna, India}
{Upwork \& Personal Projects}{05/2020 – 12/2021}
\resumeItemListStart
\resumeItem{} {Developed a blogging app for Shree Books Publications, focusing on front-end and back-end integration.}
\resumeItem{} {Enhanced skills in HTML, CSS, JavaScript, and backend technologies while delivering tailored client solutions.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------Projects-----------------
\section{Projects}
\resumeSubHeadingListStart
\resumeSubItem{\href{https://warcat.tripura.gov.in/}{Warcat Security System}}{Task tracking and report generation system with advanced features for the state of Tripura.}
\resumeSubItem{\href{https://mms.tripura.gov.in/}{Mukhya Mantri Samipeshu}}{This platform aims to register your Citizen's Representation and assist in its redressal.}
\resumeSubItem{\href{https://park-management-fe.vercel.app/}{Park Management System}}{Platform for managing event, parking, and ticketing services.}
\resumeSubItem{\href{https://slikmanagement-fe.vercel.app/}{Silk Samagra Management System}}{Component-wise fund release tracking under Silk Samagra}
\resumeSubItem{\href{https://www.npmjs.com/package/expressive-error-handler}{Expressive Error Handler (NPM Package)}}{Middleware for synchronous error handling in Express.js using \texttt{catchSyncError}. (Open Source)}
\resumeSubItem{\href{https://shreebooks.vercel.app/}{Shree Books Publications}}{Book Sale Advertisement App built with Next.js, integrating user management and content publishing. (Freelance)}
\resumeSubHeadingListEnd

%-----------Education-----------------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{I K Gujral Punjab Technical University}{Punjab, India}
{B.Tech in Electronics and Communication Engineering}{2013 - 2017}
\resumeSubHeadingListEnd

%-------Certifications------------------
\section{Certifications}
\resumeSubHeadingListStart
\resumeSubItem{}{Full Stack Web Development}
\resumeSubHeadingListEnd

%-------Languages------------------
\section{Languages}
\resumeSubHeadingListStart
\resumeSubItem{}{\textbf{Hindi:} Native | \textbf{English:} Intermediate}
\resumeSubHeadingListEnd

\end{document}
